### 2025-08-20 multiple-regression.qmd
20250820 - tweaks

Pairwise deletion (also called available case analysis) uses all available data for each pair of variables when estimating the covariances, and the resulting covariance matrix can be used to estimate a multiple regression model.
We can estimate a regression model that uses pairwise deletion using the `lavaan` package [@Rosseel2012_packages; @R-lavaan].

@@

- columns with non-zero values are [predictors](#sec-correlationalStudy) of the variable specified in the given row
- the diagonal of the predictor matrix should be zero because a variable cannot predict itself

>>>>

Pairwise deletion (also called available case analysis) uses all available data for each pair of variables when estimating the correlations/covariances, and the resulting correlation/covariance matrix can be used to estimate a multiple regression model.
We can estimate a regression model that uses pairwise deletion using the `lavaan` package [@Rosseel2012_packages; @R-lavaan].

@@

- rows with non-zero values are the target variables to be imputed
- columns with non-zero values are [predictors](#sec-correlationalStudy) of the variable specified in the given row
- the diagonal of the predictor matrix should be zero because a variable cannot predict itself
